Model LF

### 2022-12-08 Power point test.Rmd
Commit

@@

shock= ts(c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens_3=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

@@

@@

#S_modelData$xk_ds_disc = xk_ds

@@

```{r}
S_model$modelData <- within(S_model$modelData,{
  aa_check  = TSEXTEND(aa_check,  UPTO=c(2020,3))
})

S_model$modelData$aa_check
```

@@

@@

@@

>>>>

genial_dummy_shock=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2019,4), dummy_end = c(2020,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

Genial_dummy= ts(c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens_3=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

##### Shock pp

shock_pp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1 & shock_wage_ds_model > 0 & genial_dummy <=0
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 & genial_dummy <=0
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1 & genial_dummy <=0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD4 >=1 & shock_wage_ds_model > 0 & genial_dummy >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD4 >=1 & shock_wage_ds_model > 0 & genial_dummy >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1 & shock_wage_ds_model > 0 & genial_dummy >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 & genial_dummy >= 1

COMMENT> 
IDENTITY> genial_dummy
EQ> genial_dummy = genial_dummy*1
IF> shock_pp_model <= 0
IDENTITY> genial_dummy
EQ> genial_dummy = genial_dummy_shock
IF> shock_pp_model > 0

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_pp_model
EQ> shock_pp_model = shock_pp_model*1

@@

  ## pp var

   shock_pp_model = TIMESERIES(c(shock_pp_model),   
                       START=c(2005,2),FREQ=4),
  genial_dummy = TIMESERIES(c(Genial_dummy),   
                       START=c(2005,2),FREQ=4),
  genial_dummy_shock = TIMESERIES(c(genial_dummy_shock),   
                       START=c(2005,2),FREQ=4),

@@

S_modelData$genial_dummy_shock = genial_dummy_shock

@@

@@

```{r}
plot(wage_ds_t_bs2, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
lines(wage_ds_t, col="red")
grid()
```

@@

```{r}
shock_reg_model_shock=shock_reg_model %>% window(start= c(2016,1))
```

@@

```{r}
par(mfrow=c(1,2))

plot(((wage_ds_t_02 - wage_ds_t_bs2) / wage_ds_t_bs2)*100, col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()

plot(((wage_ds_02 - wage_ds_bs2) / wage_ds_bs2)*100, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
grid()

plot(((pc_ds_02 - pc_ds_bs2) / pc_ds_bs2)*100, col= "black", xlab= "Year", ylab= "% Change in consumer prices", main= "Consumer prices");
grid()
```

**Level**

```{r}
par(mfrow=c(1,2))

plot(((pconk_ds_02 - pconk_ds_bs2)), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_02 - ik_bs2)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

```{r}
par(mfrow=c(1,2))

plot(((net_balance_02 - net_balance_bs2)), col= "black", xlab= "Year", ylab= "change in net exports", main= "Net-exports");
grid()

plot(((yk_ds_02 - yk_ds_bs2)), col= "black", xlab= "Year", ylab= "Change in GDP", main= "GDP");
grid()
```

```{r}
plot(((u_ds_02 - u_ds_bs2)), col= "black", xlab= "Year", ylab= "Ændring i capacaty utilization", main= "Capacity utilization");
grid()
```

Effect on employment:

```{r}
plot((unemp_02-unemp_bs2)*1000, col= "red")
```

# Wage_ds Bs_adj

```{r}
shock_pp_model_shock=shock_pp_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs2b <- list(

 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_pp_model = TIMESERIES(shock_pp_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
Shock_bs2b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs2b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs2b = Shock_bs2b$simulation$max_dp
wage_bs2b = Shock_bs2b$simulation$wage
komp_r_bs2b = Shock_bs2b$simulation$komp_r
part_bs2b = Shock_bs2b$simulation$part
yk_ds_bs2b = Shock_bs2b$simulation$yk_ds
pc_ds_bs2b = Shock_bs2b$simulation$pc_ds
wage_ds_t_bs2b = Shock_bs2b$simulation$wage_ds_t
ur_ds_bs2b = Shock_bs2b$simulation$ur_ds
emp_bs2b = Shock_bs2b$simulation$emp
yd_hk_ds_bs2b = Shock_bs2b$simulation$yd_hk_ds
pconk_ds_bs2b= Shock_bs2b$simulation$pconk_ds
tilpas_pr_bs2b = Shock_bs2b$simulation$tilpas_pr
u_ds_bs2b = Shock_bs2b$simulation$u_ds
part_bs2b = Shock_bs2b$simulation$part
nben_h_bs2b = Shock_bs2b$simulation$nben_h
wage_ds_bs2b = Shock_bs2b$simulation$wage_ds
dp_person_bs2b = Shock_bs2b$simulation$dp_person
kont_h_ratio_bs2b = Shock_bs2b$simulation$kont_h_ratio
unemp_bs2b = Shock_bs2b$simulation$unemp
nl_g_bs2b = Shock_bs2b$simulation$nl_g
inflation_bs2b = Shock_bs2b$simulation$inflation
lf_bs2b = Shock_bs2b$simulation$lf
yd_hk_ds_bs2b = Shock_bs2b$simulation$yd_hk_ds
wage_gap1_bs2b = Shock_bs2b$simulation$wage_gap1
wage_gap_bs2b = Shock_bs2b$simulation$wage_gap
prod_bs2b = Shock_bs2b$simulation$prod
prod_bs2b = Shock_bs2b$simulation$prod
ws_bs2b = Shock_bs2b$simulation$ws
xk_ds_bs2b = Shock_bs2b$simulation$xk_ds
mk_ds_bs2b = Shock_bs2b$simulation$mk_ds

net_balance_bs2b = xk_ds_bs2b - mk_ds_bs2b
net_balance_bs2b_ratio= (xk_ds_bs2b - mk_ds_bs2b)/yk_ds_bs2b

ik_bs2b = Shock_bs2b$simulation$ik
mk_bs2b = Shock_bs2b$simulation$mk

ik_ratio_bs2b = ik_bs2b/yk_ds_bs2b
mk_ratio_bs2b = mk_bs2b/yk_ds_bs2b

c_ratio_bs2b = pconk_ds_bs2b/yk_ds_bs2b
```

```{r}
plot(wage_ds_t_bs2b, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
lines(wage_ds_t, col="red")
grid()
```

```{r}
shock_reg_model_shock=shock_reg_model %>% window(start= c(2016,1))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList2b <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_pp_model = TIMESERIES(shock_pp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_2b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList2b
                    )
```

yk_ds_02b = Shock_2b$simulation$yk_ds
emp_02b = Shock_2b$simulation$emp
wage_ds_02b = Shock_2b$simulation$wage_ds
ur_ds_02b = Shock_2b$simulation$ur_ds
pc_ds_02b = Shock_2b$simulation$pc_ds
yd_hk_ds_02b = Shock_2b$simulation$yd_hk_ds
pconk_ds_02b = Shock_2b$simulation$pconk_ds
komp_r_02b = Shock_2b$simulation$komp_r
max_dp_02b = Shock_2b$simulation$max_dp
nben_h_02b = Shock_2b$simulation$nben_h
yd_hk_ds_02b = Shock_2b$simulation$yd_hk_ds
ik_02b = Shock_2b$simulation$ik
wage_ds_t_02b = Shock_2b$simulation$wage_ds_t
nben_h_un_02b = Shock_2b$simulation$nben_h_un
nl_g_02b = Shock_2b$simulation$nl_g
nsben_h_02b = Shock_2b$simulation$nsben_h
dp_person_02b = Shock_2b$simulation$dp_person
xk_ds_02b = Shock_2b$simulation$xk_ds
mk_ds_02b = Shock_2b$simulation$mk_ds
ik_02b = Shock_2b$simulation$ik
rer_02b = Shock_2b$simulation$rer
ps_ds_02b = Shock_2b$simulation$ps_ds
i_bd_nfc_k_ds_02b = Shock_2b$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02b = Shock_2b$simulation$yd1_hk_ds
yd2ba_hk_ds_02b = Shock_2b$simulation$yd2ba_hk_ds
yd2bb_hk_02b = Shock_2b$simulation$yd2bb_hk
i_equip_nfc_k_ds_02b = Shock_2b$simulation$i_equip_nfc_k_ds
u_ds_02b = Shock_2b$simulation$u_ds
wage_gap1_02b = Shock_2b$simulation$wage_gap1
gk_02b = Shock_2b$simulation$gk
kont_h_ratio_02b = Shock_2b$simulation$kont_h_ratio
lf_02b = Shock_2b$simulation$lf
wage_gap_02b = Shock_2b$simulation$wage_gap
max_gap_02b = Shock_2b$simulation$max_gap
unemp_02b = Shock_2b$simulation$unemp
inflation_02b = Shock_2b$simulation$inflation
prod_02b = Shock_2b$simulation$prod
ws_02b = Shock_2b$simulation$ws
net_balance_02b = xk_ds_02b - mk_ds_02b
```

```{r}
par(mfrow=c(1,2))

plot(((wage_ds_t_02b - wage_ds_t_bs2b) / wage_ds_t_bs2b)*100, col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()

plot(((wage_ds_02b - wage_ds_bs2b) / wage_ds_bs2b)*100, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
grid()
